My Master thesis

### 2020-01-28 manuscript/index/05-appendix.Rmd
- notes 23-01 - update table - add bookdown

---
title: "Definition list"
author: "Gerbrich Ferdinands"
date: "1/20/2020"
output: pdf_document
---

>>>>

`r if(knitr:::is_latex_output()) '\\appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

<!--
If you feel it necessary to include an appendix, it goes here.
-->

# The First Appendix

This first appendix includes all of the R chunks of code that were hidden throughout the document (using the `include = FALSE` chunk tag) to help with readibility and/or setup.

**In the main Rmd file**

```{r ref.label='include_packages', results='hide', echo = TRUE}
```

**In Chapter \@ref(ref-labels):**

```{r ref.label='include_packages_2', results='hide', echo = TRUE}
```

# List of definitions

Epoch
:  A particular
